Visualising CHD Pathway Inequalities by ethnicity - DRAFT

### 2024-04-23 draft_report.qmd
Style table of imd by cluster

Table 3 = imd

>>>>

Table 3 shows that

patientweighted_practice_imd |>
  mutate(gp_imd_quantile = case_when(gp_imd_decile<=2 ~ 1,
                                     gp_imd_decile==3 ~2,
                                     gp_imd_decile==4 ~2,
                                     gp_imd_decile==5 ~3,
                                     gp_imd_decile==6 ~3,
                                     gp_imd_decile==7 ~4,
                                     gp_imd_decile==8 ~4,
                                     gp_imd_decile>=9 ~5,
                                     .default = 0
  ))|>
  group_by(gp_imd_quantile,cluster)|>
  summarise(patients=sum(patients))|>
  ungroup()|>
  group_by(cluster)|>
  mutate(cluster_total=sum(patients),
         perc=patients/cluster_total)|>
  select(-patients,-cluster_total)|>
  pivot_wider(names_from=c(cluster),
              names_sep = "_",
              values_from = perc
  )|>
  select(gp_imd_quantile, starts_with("1"), starts_with("2"), starts_with("3"),starts_with("4"),starts_with("5")) |>
  arrange(factor(gp_imd_quantile, 
                 levels = c("1","2","3","4","5")))|>

  gt(rowname_col = "gp_imd_quantile")|>
  tab_stubhead(label=md("**IMD Quantile**"))|>
  tab_options(heading.title.font.size = 18,
              heading.title.font.weight = "bolder",
              column_labels.font.weight = "bold")|>
    tab_stubhead(label=md("**IMD Quantile**"))|>
  fmt_percent(columns=c(starts_with("1"), starts_with("2"), starts_with("3"),starts_with("4"),starts_with("5")),decimals = 2)|>
  tab_header(title = md("**Table 3** - *Index of Multiple Deprivation Breakdown by Cluster*"))
```
